Figures

### 2018-10-26 figures/04_nlcd-versus-cdl.Rmd
include pasture in cdl total ag

```{r 04_nlcd-versus-cdl, fig.height=3, echo=FALSE}
library(LAGOSNE)
library(ggplot2)
library(HydroData)
library(dplyr)
library(tidyr)

cdl <- read.csv("../data/cdl/cdl_summary.csv", stringsAsFactors = FALSE) %>%
  dplyr::select(lagoslakeid = llid, cdl_ag_99 = ag, cdl_pasture_81 = pasture)

@@

ggplot(data = res, aes(x = nlcd, y = cdl)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1) +
  facet_wrap(~variable)
```

>>>>

```{r 04_nlcd-versus-cdl, fig.height=3, echo=FALSE}
library(LAGOSNE)
library(ggplot2)
library(HydroData)
library(dplyr)
library(tidyr)
# setwd("data")
cdl <- read.csv("../data/cdl/cdl_summary.csv", stringsAsFactors = FALSE) %>%
  dplyr::select(lagoslakeid = llid, cdl_ag_99 = ag, cdl_pasture_81 = pasture)

@@

ggplot(data = res, aes(x = nlcd, y = cdl)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1) +
  facet_wrap(~variable) +
  theme_minimal()
```
